Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
pass on examples

\sloppy
\vspace{1ex}\noindent\textbf{Issue \#4, Table~\Fix{XX}.} The code
snippet below shows the test input we used to reveal a bug in
\chakra.

@@

The object property \CodeIn{valueOf} stores a function
that returns a primitive value identifying the target
object~\cite{valueof}. The original version of this code returns an
empty string whereas the version of the code modified by the \radamsa{}
fuzzer~\cite{radamsa} returns a string representation of a null
character (\CodeIn{NUL} in ascii). The unary plus expression
``\CodeIn{+a}", used in the assertion, is equivalent to the operation
\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)\cite{unary-plus}. For this case, \chakra{}\Mar{\chakra? if
  chakra did that it would be fine, no?} \Igor{
  \chakra{} converte incorretamente o valor hexadecimal para
  0 e a expressao +0 resulta em 0, o que faz com que o teste passe. Os outros
  engines consideram o hexadecimal invalido (valor esperado), 
  quando o hexadecimal nao pode ser convertido, espera-se que retorne NaN, que +NaN resulta em NaN.
  }evaluates the unary
plus to NaN as expected, as the null character cannot be converted. As
result, the test fails as expected. \chakra{}, in contrast,
incorrectly converts the string to zero, making the test to pass. All
other engines fail on this test. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.

\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.}
\Igor{
  Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
  Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
  que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
  de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
  that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
  B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
  function declaration. The fuzzer removes the function declaration and 
  injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
  the break statement should throw an early error (in this case a SyntaxError) 
  if the break statement is not nested in an iterational or a switch statement. All engines works
  as expected but \veight{} pass without failures.
}

@@

\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:test-transplantation-bugs}.}
Esse bug foi reportado no engenho do \chakra{} e foi manifestado atraves 
de uma mutacao provinda do \radamsa{}. O test case eh descrito in Figure~\ref{xxx},
the

>>>>

\sloppy
\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
code snippet below shows the test input we used to reveal a bug in
\chakra.

@@

The object property \CodeIn{valueOf} stores a function that returns a
primitive value identifying the target object~\cite{valueof}. The
original version of this code returns an empty string whereas the
version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
returns a string representation of a null character (\CodeIn{NUL} in
ascii). The unary plus expression ``\CodeIn{+a}", used in the
assertion, is equivalent to the operation
\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)~\cite{unary-plus}. This test fails in all engines but
\chakra{}. For all three engines the string cannot be parsed as an
hexadecimal. As such, they produce a NaN as result and the test fails
as expected. \chakra{}, in contrast, incorrectly converts the string
to zero, making the test to pass. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.

\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.}  The
code snippet below shows the test input we used to reveal a bug in
\veight{}.

@@

\vspace{1ex}\noindent\textbf{Issue \#2,
  Table~\ref{tab:test-transplantation-bugs}.}  The code snippet below
shows the test input we used to reveal a bug in \jsc{}. This test
originates from \jerry{} test suite; the bug was found during the test
transplantation experiment.

\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function, 
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
var obj = {}; var arr = [];
try {
  arr.sort(obj);
  assert(false);
} catch (e) {
  assert(e instanceof TypeError);
}
  \end{lstlisting}
  \normalsize
  %% \caption{Warning captured as \hi{} priority.}
  %% \label{fig:hi-priority}
\end{figure}

According to the specification~\cite{ecmas262-array-sort}, the
parameter to the \CodeIn{Array.sort} function should be a comparable
object or an undefined value, otherwise it should throw a
\CodeIn{TypeError}. In this case, \jsc{} accepts a non-callable object
as argument to \CodeIn{sort} and the test fails in the subsequent
step. The other engines raise a \CodeIn{TypeError} as expected.
